Reproducible Research / Peer Assessment 1
=========================================

## Loading and preparing Data
```{r}
actData=read.csv("activity.csv")
goodOnes=complete.cases(actData)
cleanData=actData[goodOnes,]
cleanData$date=as.factor(as.character(cleanData$date)) #removing entries of date 

Sys.setlocale("LC_TIME", "English")
library(chron)

```
## What is mean total number of steps taken per day?
````{r}
dayTotal=tapply(cleanData$steps,cleanData$date,sum,simplify=TRUE)
hist(dayTotal,breaks=10,col="RED")
```
### Mean and Median
```{r}
dayMean=tapply(cleanData$steps,cleanData$date,mean,simplify=TRUE)
dayMedian=tapply(cleanData$steps,cleanData$date,median,simplify=TRUE)
```

### What is the average daily activity pattern?
```{r}
intervalMean=tapply(cleanData$steps,cleanData$interval,mean,simplify=TRUE)
plot(intervalMean,t="l",xlab="Interval average over all days")
```

### Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
names(which(intervalMean==max(intervalMean))) #name of interval with max avarage steps
sum(!goodOnes) #number of missing entries


```
### Imputing missing values
```{r}
naIndex=which(is.na(actData$steps))
for (i in seq_along(naIndex)){
  actData[naIndex[i],1]=as.integer(intervalMean[as.character(actData[naIndex[i],3])])
}

dayTotal2=tapply(actData$steps,actData$date,sum,simplify=TRUE)
hist(dayTotal2,breaks=10,col="RED")
dayMean2=tapply(actData$steps,actData$date,mean,simplify=TRUE)
dayMedian2=tapply(actData$steps,actData$date,median,simplify=TRUE)
intervalMean2=tapply(actData$steps,actData$interval,mean)
plot(intervalMean2,t="l",xlab="Interval average over all days")
```
### What is the impact of imputing missing data on the estimates of the total daily number of steps?
```{r}
sum(dayTotal)-sum(dayTotal2)
```
### Are there differences in activity patterns between weekdays and weekends?
```{r}

actData$day=as.factor(ifelse(is.weekend(as.Date(actData$date)),"Weekend", "Weekdays"))

byDays=with(actData, tapply(steps, list(day,interval),mean))

#byDays=rbind(byDays,as.integer(colnames(byDays)))

par(mfrow=c(2,1), mar=c(2,2,2,1))
plot(byDays[1,],t="l",main="weekdays",ylab="Number of steps",xlab="Interval",cex.lab=0.7,cex.axis=0.8)
plot(byDays[2,],t="l",main="weekend",ylab="Number of steps",xlab="Interval",cex.lab=0.7,cex.axis=0.8)
```
